---
title: "Getting started with binomial"
author: "Isaac Schmidt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Statistics of the Binomial Distribution

```{r}
my_bin = bin_variable(trials=7,prob=.25)
my_bin
```

The function `bin_variable` takes two arguments, `trials` and `prob`, and returns an instance of a binomial random variable. The most useful thing to do with a binomial random variable is to see its summary statistics, such as mean and variance.

```{r}
summary(my_bin)
```

Alternatively, you can calculate a certain statistic directly.

```{r}
bin_variance(trials=7,prob=.25)
```

## Probabilities

To get the probability that a binomial random variable with parameters n and p equals k, use `bin_probability`.

```{r}
bin_probability(success=3,trials=10,prob=1/3)
```

You can pass in multiple values to `success` as a vector.

```{r}
bin_probability(success=1:3,trials=5,prob=0.5)
```

To get all probabilities for a certain `trials` and `prob`, use `bin_distribution`.

```{r}
my_bindis = bin_distribution(trials=7,prob=.25)
my_bindis
```

To see the cumulative distribution, use `bin_cumulative`.

```{r}
my_bincum = bin_cumulative(trials=7,prob=.25)
my_bincum
```

## Plotting

You can easily plot both the binomial distribution and binomial cumulative distribution.

```{r,fig.show='hold'}
plot(my_bindis)
```

```{r, fig.show='hold'}
plot(my_bincum)
```

